Evaluating the evidence of widespread maintenance of functional composition in vertebrate communities

### 2021-10-08 paper/manuscript.Rmd
BEF paragraph! At long last!

We observed no significant trends within taxa No significant differences between taxa.
Indicates that we could've looked at any taxonomic subset of the data and gotten the same result.
But what does that mean for taxa we left out?
We can only make educated guesses based on what we know of the ecology of taxa that were left out - taxa specific papers?

What does local maintenance of functional structure mean for the function of these communities?
The vast majority of experimental and observational work links declines in function to declines in functional or species diversity [@brose2016; @cadotte2011; @duffy2007] .
By those criteria, very few observed communities in our dataset are in a state of concern for loss of functionality.
However, we did not directly measure some aspects of community structure important for ecosystem multifunctionality [e.g.
dispersion, rarity, abundance of dominant species; @bagousse-pinguet2021].
While our metrics indirectly incorporate dimensions of the functional space related to those community characteristics, they are likely not sensitive enough to infer deterioration (or improvement).
<!-- more citations please --> This highlights the need for further development of theory linking different aspects of functional change to specific implications for function.

-   experiments vs broad scale observational studies - do we look at FD in both?

<!-- any work looking at function in communities that are stable along these axes? -->

@@

>>>>

@@

What does local maintenance of functional structure mean for ecosystem function?
The vast majority of experimental and observational work links declines in function to declines in functional or species diversity [@brose2016; @cadotte2011; @duffy2007]. By those criteria very few communities in our dataset are in a state of concern for loss of functionality. However, the dimensions of functional space most important for ecosystem function are still a topic of on going debate, and at least some known aspects important for multifunctionality were not measured here [e.g. dispersion, rarity, abundance of dominant species; @bagousse-pinguet2021]. The fact that we observed so many communities maintaining structure across the most commonly used metrics for linking biodiversity to function calls into question how previous work translates to natural communities.
Metrics need to be both closely linked to changes in ecosystem function and also experiencing shifts in natural communities to be meaningful.

<!-- We observed no significant trends within taxa. Even Amphibians, considered highly sensitive to human impact, maintained functional structure through time.  Indicates that we could've looked at any taxonomic subset of the data and gotten the same result. But what does that mean for taxa we left out? We can only make educated guesses based on what we know of the ecology of taxa that were left out - taxa specific papers? -->
